\plaintitle

### 2016-09-21 drafts/labor/cases.tex
decomposition revised
moved a bunch of piecework history to its constituent sections. exciting!

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Major Research Questions}

@@

\endnotetext{
Here, \citeauthor{hu1961parallel}'s work,  saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',  parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,  and indeed the study of factory and mass manufacturing labor through the \nth{20} century,  substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,  and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

Piecework's influence on the abstraction of work into tasks,  described above, is more than just caused by the decomposition of work;
work abstraction itself makes it possible for workers to come and go flexibly,  prompting work requesters to consider ways to design these now discrete tasks in ways that
maximize flexibility, both by allowing (and even anticipating) some inconsistency in worker availability
\textit{and} allowing and anticipating some inconsistency in the quality of the work output itself.
It's to this area that we now turn our attention.

Piecework has seen work along this dimension spanning decades;
\citeauthor{thompson1913time} investigate some of the ways that
construction can benefit from the principles of scientific management.
\citeauthor{thompson1913time}'s thesis asserts that
task work is predicated on the accurate scientific management of work,  including the ``miscellaneous tasks''.
\citeauthor{thompson1913time} argues
--- as early as \citeyear{thompson1913time} ---
that ``\dots one may be challenged to find any class of work
involving labor either indoors or out--of--doors
where tasks cannot be fixed by proper time--study''
\cite{thompson1913time}.

Broken down in this way, work could grow to unprecedented scales,  but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example,  it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,  manageable routines that could be taught relatively easily,  and whose work output could be evaluated in abstraction from the rest of the work
\cite{restructuringPieceworkBaker}.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,  but a single very narrowly defined action that needed to be done on every car
\cite{towardsGlobalFordism}.
By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes,  ``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''
\cite{schoenberger1988fordism}.

This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos),  can be seen today in crowd work and on--demand labor through the application of micro--tasks.
\citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces,  facilitating evaluation and parallelization
\cite{writingMicroTasks}.
By decomposing and recomposing tasks,  and in particular by assigning similarly natured work to the same workers,  workers could become ``experts'' in a small aspect of the work that they did,  speeding their work dramatically
\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage
\cite{rogstadius2011assessment}.

\subsubsection{So how does this affect crowd work?}
The work we've seen so far 
\begin{itemize}
  \item worst case: assembling iPhones (extant)
  \item average case: railroad workers and assembly lines
  \item high (complexity) case: 
\end{itemize}

% so CW?
% mechanism/limitation in pw?
% differences in cw? tech/access to intelligence?
% predicted outcome then? -> decompose effort/expertise access
% possible quirks/diffs?

% what can be decomposed? what can be evaluated?
% technology/turuing completeness gets us a win
% predefined expertise? you can find someone almost instantly;
% ease of doing this makes it qualitatively different due to Channel Factors (diverting a channel/river)
% huddler paper cites some decomposition stuff workflows are good/bad at things
% 3-way slack w/msb and mav
% academy of management 
% van der ven paper ~1972 limits of workflows cited in daniela's flash orgs paper
}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Research Questions}

@@

% \endnotetext{
% Here, \citeauthor{hu1961parallel}'s work,  saying of assembly line work that
% ``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',  parallels the approach that dominated early research into crowd work
% --- namely, using non--expert crowds for complex work
% \cite{hu1961parallel}.
% This mindset in \citeauthor{hu1961parallel}'s analysis,  and indeed the study of factory and mass manufacturing labor through the \nth{20} century,  substantively owes its existence to scientific management
% and the rigorous decomposition of work into tasks, discussed earlier,  and persists to this day as it colors
% researchers' goals and objectives in the study and design of crowd work.

% Piecework's influence on the abstraction of work into tasks,  described above, is more than just caused by the decomposition of work;
% work abstraction itself makes it possible for workers to come and go flexibly,  prompting work requesters to consider ways to design these now discrete tasks in ways that
% maximize flexibility, both by allowing (and even anticipating) some inconsistency in worker availability
% \textit{and} allowing and anticipating some inconsistency in the quality of the work output itself.
% It's to this area that we now turn our attention.

% Piecework has seen work along this dimension spanning decades;
% \citeauthor{thompson1913time} investigate some of the ways that
% construction can benefit from the principles of scientific management.
% \citeauthor{thompson1913time}'s thesis asserts that
% task work is predicated on the accurate scientific management of work,  including the ``miscellaneous tasks''.
% \citeauthor{thompson1913time} argues
% --- as early as \citeyear{thompson1913time} ---
% that ``\dots one may be challenged to find any class of work
% involving labor either indoors or out--of--doors
% where tasks cannot be fixed by proper time--study''
% \cite{thompson1913time}.

% Broken down in this way, work could grow to unprecedented scales,  but the quality of the work would remain relatively variable
% \cite{murray1983decentralisation}.
% Textile work being a salient example,  it took time for workers to acquire sufficient skill
% to do every aspect of the work so that the garment would be accepted by the company soliciting that work
% \cite{vezina1992light}.

% A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,  manageable routines that could be taught relatively easily,  and whose work output could be evaluated in abstraction from the rest of the work
% \cite{restructuringPieceworkBaker}.
% In Ford's assembly line, this meant that workers were not responsible for building a whole car,  but a single very narrowly defined action that needed to be done on every car
% \cite{towardsGlobalFordism}.
% By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes,  ``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''
% \cite{schoenberger1988fordism}.

% This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos),  can be seen today in crowd work and on--demand labor through the application of micro--tasks.
% \citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces,  facilitating evaluation and parallelization
% \cite{writingMicroTasks}.
% By decomposing and recomposing tasks,  and in particular by assigning similarly natured work to the same workers,  workers could become ``experts'' in a small aspect of the work that they did,  speeding their work dramatically
% \cite{delayAndOrderLasecki}.
% Perhaps more important, however, was that
% the breaking down of work into tasks has made it more practical to evaluate work at each stage
% \cite{rogstadius2011assessment}.

% \subsubsection{So how does this affect crowd work?}
% The work we've seen so far 
% \begin{itemize}
%   \item worst case: assembling iPhones (extant)
%   \item average case: railroad workers and assembly lines
%   \item high (complexity) case: 
% \end{itemize}

% % so CW?
% % mechanism/limitation in pw?
% % differences in cw? tech/access to intelligence?
% % predicted outcome then? -> decompose effort/expertise access
% % possible quirks/diffs?

% % what can be decomposed? what can be evaluated?
% % technology/turuing completeness gets us a win
% % predefined expertise? you can find someone almost instantly;
% % ease of doing this makes it qualitatively different due to Channel Factors (diverting a channel/river)
% % huddler paper cites some decomposition stuff workflows are good/bad at things
% % 3-way slack w/msb and mav
% % academy of management 
% % van der ven paper ~1972 limits of workflows cited in daniela's flash orgs paper
% }

### 2016-09-21 drafts/labor/complexity.tex
decomposition revised
moved a bunch of piecework history to its constituent sections. exciting!

\subsubsection[What are the limits of crowd work]{Identifying the Limits of Crowd Work}\label{sec:complexity}
\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

@@

\subsubsubsection{\pieceworkpers}
\topic{Piecework researchers have found themselves trying to understand what characteristics limit piecework,
or more precisely what has prevented piecework from becoming more prevalent.}
The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} reports on the hiring of Harrington Emerson,
an ``efficiency expert'', who went on to develop a ``standard time'' for each task at the company
informed by ``thousands of individual operations at the Topeka shops''.
The cost of measuring workers in such excruciating detail at the turn of the \nth{20} century was undoubtedly immense,
but this ``standard time'' value, which determined the pay that workers would earn for each task they do,
was the only viable approach at the time to determine appropriate pay given the task
\cite{10.2307/23702539}.
But the repeated measurement of workers' time to complete tasks had shortcomings;
for one thing, pay rates for rarer tasks
were necessarily less certain than for more common tasks,
which had the simple benefit of a larger sample size.
\ali{Do I need ``for another thing\dots''? This paragraph is kind of huge already. Not sure how to break it up/down as it is.}
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work --- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.

@@

\subsubsubsection{\whatchanged}
\msb{Before you get into this, summarize what I am supposed to have learned from the prior section on piecework.
You're about to draw on those points to make your argument, so they need to be at the top of my mind here.}
\topic{Piecework makes a number of observations leading to the conclusion that
piecework's complexity is fundamentally bounded by several limitations,
chief among them the costs of managerial overhead and the transition thereto.}
\citeauthor{Brown01041990} and \citeauthor{10.2307/23702539}'s claims that
organizations can't adopt piecework unless
they're sufficiently large to absorb the cost of transitioning to a piecework system;
\citeauthor{10.2307/2118435} and \citeauthor{wray1949marginal}'s observations for
the importance of competent, effective managerial oversight
--- a human resource, which made the scaling cost prohibitively expensive for many
% in their times (\citeyear{10.2307/2118435} and \citeyear{wray1949marginal}, respectively)
\cite{10.2307/2118435,wray1949marginal,10.2307/23702539,Brown01041990}.
\ali{Something like this? Should I dig deeper?
I can line these points up in a way to make the next paragraph sort of obvious or inevitably,
depending on how actively engaged someone is while reading this\dots}

@@

\subsubsubsection{\implication}
\msb{This paragraph can be expanded to make a more concrete argument. What will be possible? What won't?}
\topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
it also signals some of the ultimate limitations of crowd work and piecework in general.}
While the threshold preventing task requesters from utilizing piecework
has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly. \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}

>>>>

\subsection[What are the limits of crowd work]{Identifying the Limits of Crowd Work}\label{sec:complexity}
\subsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

@@

\subsubsection{\pieceworkpers}
\topic{First largely used among farm workers, as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it was brought to the textile industry
\cite{hughRaynbirdTaskWork}.}
At the turn of the \nth{20} century,
when \citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City,
\citeauthor{norton1900textile} was providing substantive guidance on various wage regimes,
\cite{riisOtherSideLives,norton1900textile}.

\topic{Piecework then began to grow: first applied to farm work, as
\citeauthor{hughRaynbirdTaskWork} and others illustrate,
the practice remained relatively obscure until
it blossomed in the textile industry
\cite{hughRaynbirdTaskWork}.}
This growth was so marked that by the turn of the \nth{20} century,
\citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City,
and \citeauthor{norton1900textile} was providing substantive guidance on various wage regimes,
offering guidance on how best to manage pieceworkers
\cite{riisOtherSideLives,norton1900textile}.
\citeauthor{clark1908cotton}, for instance,
relays his observations of textile mill pieceworkers and his realization that
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''
\cite{clark1908cotton}.
During this period, best practices regarding the measurement and management of
piecework rates, and of workers in the engineering industry,
were beginning to take shape
\cite{burton1899commercial}.
% \ali{Everything up till now has been pointing at complexity (right? if not, then~\dots~lol)}

\topic{Researchers sought to understand the characteristics of piecework
that fueled its rise to popularity.}
\citeauthor{10.2307/23702539} argued that the first sparks of scientific management
could be found in piecework;
the approach of paying workers for each piece of output necessitated
the rigorous tracking, measurement, and training of workers
for which scientific management became famous
\cite{10.2307/23702539}.
This argument is certainly compelling;
it would seem to make the concurrent upswing of
scientific management and Fordism
through the first two--thirds of the \nth{20} century
alongside piecework not only understandable, but predictable
\cite{hart2013rise}.
\citeauthor{Brown01041990} inquired from another direction, asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined, this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically, the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework
\cite{Brown01041990}.
% \ali{that last paragraph is a mix of complexity and decomposition I think}

\topic{Piecework researchers have found themselves trying to understand what characteristics limit piecework,
or more precisely what has prevented piecework from becoming more prevalent.}
The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} reports on the hiring of Harrington Emerson,
an ``efficiency expert'', who went on to develop a ``standard time'' for each task at the company
informed by ``thousands of individual operations at the Topeka shops''.
The cost of measuring workers in such excruciating detail at the turn of the \nth{20} century was undoubtedly immense,
but this ``standard time'' value, which determined the pay that workers would earn for each task they do,
was the only viable approach at the time to determine appropriate pay given the task
\cite{10.2307/23702539}.
But the repeated measurement of workers' time to complete tasks had shortcomings;
for one thing, pay rates for rarer tasks
were necessarily less certain than for more common tasks,
which had the simple benefit of a larger sample size.
\ali{Do I need ``for another thing\dots''? This paragraph is kind of huge already. Not sure how to break it up/down as it is.}
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work --- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.

@@

\subsubsection{\whatchanged}
\msb{Before you get into this, summarize what I am supposed to have learned from the prior section on piecework.
You're about to draw on those points to make your argument, so they need to be at the top of my mind here.}
\topic{Piecework makes a number of observations leading to the conclusion that
piecework's complexity is fundamentally bounded by several limitations,
chief among them the costs of managerial overhead and the transition thereto.}
\citeauthor{Brown01041990} and \citeauthor{10.2307/23702539}'s claims that
organizations can't adopt piecework unless
they're sufficiently large to absorb the cost of transitioning to a piecework system;
\citeauthor{10.2307/2118435} and \citeauthor{wray1949marginal}'s observations for
the importance of competent, effective managerial oversight
--- a human resource, which made the scaling cost prohibitively expensive for many
% in their times (\citeyear{10.2307/2118435} and \citeyear{wray1949marginal}, respectively)
\cite{10.2307/2118435,wray1949marginal,10.2307/23702539,Brown01041990}.
\ali{Something like this? Should I dig deeper?
I can line these points up in a way to make the next paragraph sort of obvious or inevitably,
depending on how actively engaged someone is while reading this\dots}

@@

\subsubsection{\implication}
\msb{This paragraph can be expanded to make a more concrete argument. What will be possible? What won't?}
\topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
it also signals some of the ultimate limitations of crowd work and piecework in general.}
While the threshold preventing task requesters from utilizing piecework
has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly. \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}

### 2016-09-21 drafts/labor/decomposition.tex
moved a bunch of piecework history to its constituent sections. exciting!

\subsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena
\cite{grier2013computers}.
%These workers became the first \textit{computers}.

>>>>

\subsubsection{\pieceworkpers}
\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories, but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter''
--- an icon of mid--\nth{20} century America who represented empowerment and opportunity for women \cite{honey1985creating} ---
was herself a pieceworker
\cite{davies2014origins}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena
\cite{grier2013computers}.
%These workers became the first \textit{computers}.

### 2016-09-21 drafts/labor/piecework_lit.tex
moved a bunch of piecework history to its constituent sections. exciting!

While piecework has been studied from myriad perspectives through the lenses of
political science,
economics (both micro-- and macro--), and
a plethora of other fields
\ali{should I cite examples of all of these?}, for the sake of brevity
we will discuss the history of piecework in the contexts of the three questions we brought up with crowd work:
``\namerefl{sec:complexity}'',
``\namerefl{sec:decomposition}'', and 
``\namerefl{sec:relationships}''.

@@

@@

\ali{I'm thinking of dropping most of the last paragraph and merging it with the next one. Thoughts?}

\ali{Complexity?}
\topic{First largely used among farm workers, as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it was brought to the textile industry
\cite{hughRaynbirdTaskWork}.}
At the turn of the \nth{20} century,
when \citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City,
\citeauthor{norton1900textile} was providing substantive guidance on various wage regimes,
\cite{riisOtherSideLives,norton1900textile}.

\ali{Complexity?}
\topic{Piecework then began to grow: first applied to farm work, as
\citeauthor{hughRaynbirdTaskWork} and others illustrate,
the practice remained relatively obscure until
it blossomed in the textile industry
\cite{hughRaynbirdTaskWork}.}
This growth was so marked that by the turn of the \nth{20} century,
\citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City,
and \citeauthor{norton1900textile} was providing substantive guidance on various wage regimes,
offering guidance on how best to manage pieceworkers
\cite{riisOtherSideLives,norton1900textile}.
\citeauthor{clark1908cotton}, for instance,
relays his observations of textile mill pieceworkers and his realization that
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''
\cite{clark1908cotton}.
During this period, best practices regarding the measurement and management of
piecework rates, and of workers in the engineering industry,
were beginning to take shape
\cite{burton1899commercial}.
% \ali{Everything up till now has been pointing at complexity (right? if not, then~\dots~lol)}

\ali{Complexity + Decomposition?}
\topic{Researchers sought to understand the characteristics of piecework
that fueled its rise to popularity.}
\citeauthor{10.2307/23702539} argued that the first sparks of scientific management
could be found in piecework;
the approach of paying workers for each piece of output necessitated
the rigorous tracking, measurement, and training of workers
for which scientific management became famous
\cite{10.2307/23702539}.
This argument is certainly compelling;
it would seem to make the concurrent upswing of
scientific management and Fordism
through the first two--thirds of the \nth{20} century
alongside piecework not only understandable, but predictable
\cite{hart2013rise}.
\citeauthor{Brown01041990} inquired from another direction, asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined, this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically, the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework
\cite{Brown01041990}.
% \ali{that last paragraph is a mix of complexity and decomposition I think}

@@

\ali{Decomposition + Relationships?}
\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories, but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter''
--- an icon of mid--\nth{20} century America who represented empowerment and opportunity for women \cite{honey1985creating} ---
was herself a pieceworker
\cite{davies2014origins}.

\ali{Relationships}
\topic{Despite the intense growth of the piecework approach to renumeration,
this time was not without turmoil.}
As previously discussed, a number of worker organizations weighed in on
(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
\cite{american1921problem,richards1904anything}.
As mounting attention increasingly revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.
\citeauthor{riisOtherSideLives}'s photo--documentary work
brought light to otherwise--invisible pieceworkers in their homes;
this and other events led to organizations representing
railway workers, mechanical engineers, and others
who began to mount advocacy in defense and favor of workers
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
\citeauthor{10.2307/3827491} tells us of the match--girls strike of 1888,
one of the earliest and most famous successful worker strikes and perhaps
the beginning of ``militant trade unionism''
\cite{10.2307/3827491}.
It wasn't an exaggeration when \citeauthor{weyer1894history} later said that
``the match--girls' victory turned a new leaf in Trade Union annals'' \cite{weyer1894history};
in the 30 years since the match--girls strike,
the Trade Union Movement grew from
``20 per cent of adult male manual--working wage--earners [to] over 60 per cent''
\cite{webb1920history}.

\ali{Relationships}
\topic{While many workers participated in piecework, worker sentiment toward the practice was --- by all accounts --- mostly negative.}
The match girls strikes which \citeauthor{10.2307/3827491} describes were just one early
--- albeit critical ---
case study in this space;
the national coal strike of 1912 led to an overwhelming vote among federated coal miner pieceworkers
to strike for
an individual minimum wage, among other demands
\cite{10.2307/2221944}.
\citeauthor{10.2307/41829256} documents a series of efforts among women in the garment industries in Philadelphia to negotiate collective bargaining rights and recognition of their own labor union
\cite{10.2307/41829256}.
The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally
\cite{jacoby1983union}.

>>>>

% While piecework has been studied from myriad perspectives through the lenses of
% political science,
% economics (both micro-- and macro--), and
% a plethora of other fields
% \ali{should I cite examples of all of these?}, for the sake of brevity
% we will discuss the history of piecework in the contexts of the three questions we brought up with crowd work:
% ``\namerefl{sec:complexity}'',
% ``\namerefl{sec:decomposition}'', and 
% ``\namerefl{sec:relationships}''.

@@

\ali{REMOVED A BUNCH OF STUFF FROM HERE ONWARD}

@@

\ali{\sout{I'm thinking of dropping most of the last paragraph and merging it with the next one. Thoughts?}
I moved it to \nameref{sec:complexity}}

@@

### 2016-09-21 drafts/labor/relationships.tex
decomposition revised
moved a bunch of piecework history to its constituent sections. exciting!

\subsubsection[What will work and the place of work look like for workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers
% with their work,
with their peers and
with requesters
are nuanced and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets;
still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{crowdcollab,miller2011understanding}.
We can break this general body of work into two subgroups:
workers' relationships
\begin{inlinelist}
% \item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

@@

\subsubsubsection{\pieceworkpers}
\topic{The questions surrounding
the ways pieceworkers related to managers might be best answered by
the work that has been done in the emergence and proliferation of labor unions.}
The primary avenue for workers to interact with managers has been through
laborer advocacy groups such as the American Federation of Labor,
(one of the forerunners of the largest and
most politically influential labor union in the United States).
Looking through that lens, we find copious research on
the relationships between workers and requesters
\cite{levi2009union,ahlquist2013interest,
      mccallum2013global,jacoby1983union}.
One component of collectively negotiating with managers has been the process
of collective action, a topic which has been substantively explored
but is not quite yet answered
\cite{russell1982collective,olsonlogic}.

@@

\subsubsubsection{\whatchanged}
\topic{The differences between crowd workers and pieceworkers seem defined largely by
the differences in the places of work.}
Whereas it arguably became inevitable that workers would have a place to
meet, discuss, and collaborate
when they began sharing places of work,
online spaces make it much harder to do so.
Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
without any affiliation with
--- or even knowledge of ---
communities of peers
% \ali{multiple citations that labor unions came out of factories here}
\cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

@@

\subsubsubsection{\implication}
\topic{What we've done in the field of crowd work might be able to tell us something about piecework
just as piecework has told us so much about crowd work.}
Crowd work research doesn't just benefit from
digital media allowing us to make
relationship networks like \citeauthor{crowdcollab} do;
we benefit from the firmer theoretical basis of Anthropology that
existed in a radically different form at the turn of the \nth{20} century,
when piecework began to emerge.
\citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works
\cite{malinowski2002argonauts,boas1940race,mead1973coming}.

>>>>

\subsection[What will work and the place of work look like for workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}

\subsubsection{\crowdworkpers}
\topic{The relationships of workers
% with their work,
with their peers and
with requesters
are nuanced and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets;
still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{crowdcollab,miller2011understanding}.
We can break this general body of work into two subgroups:
workers' relationships
\begin{inlinelist}
% \item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

@@

\subsubsection{\pieceworkpers}
\topic{Despite the intense growth of the piecework approach to renumeration,
this time was not without turmoil.}
As previously discussed, a number of worker organizations weighed in on
(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
\cite{american1921problem,richards1904anything}.
As mounting attention increasingly revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.
\citeauthor{riisOtherSideLives}'s photo--documentary work
brought light to otherwise--invisible pieceworkers in their homes;
this and other events led to organizations representing
railway workers, mechanical engineers, and others
who began to mount advocacy in defense and favor of workers
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
\citeauthor{10.2307/3827491} tells us of the match--girls strike of 1888,
one of the earliest and most famous successful worker strikes and perhaps
the beginning of ``militant trade unionism''
\cite{10.2307/3827491}.
It wasn't an exaggeration when \citeauthor{weyer1894history} later said that
``the match--girls' victory turned a new leaf in Trade Union annals'' \cite{weyer1894history};
in the 30 years since the match--girls strike,
the Trade Union Movement grew from
``20 per cent of adult male manual--working wage--earners [to] over 60 per cent''
\cite{webb1920history}.

\topic{While many workers participated in piecework, worker sentiment toward the practice was --- by all accounts --- mostly negative.}
The match girls strikes which \citeauthor{10.2307/3827491} describes were just one early
--- albeit critical ---
case study in this space;
the national coal strike of 1912 led to an overwhelming vote among federated coal miner pieceworkers
to strike for
an individual minimum wage, among other demands
\cite{10.2307/2221944}.
\citeauthor{10.2307/41829256} documents a series of efforts among women in the garment industries in Philadelphia to negotiate collective bargaining rights and recognition of their own labor union
\cite{10.2307/41829256}.
The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally
\cite{jacoby1983union}.

\topic{The questions surrounding
the ways pieceworkers related to managers might be best answered by
the work that has been done in the emergence and proliferation of labor unions.}
The primary avenue for workers to interact with managers has been through
laborer advocacy groups such as the American Federation of Labor,
(one of the forerunners of the largest and
most politically influential labor union in the United States).
Looking through that lens, we find copious research on
the relationships between workers and requesters
\cite{levi2009union,ahlquist2013interest,
      mccallum2013global,jacoby1983union}.
One component of collectively negotiating with managers has been the process
of collective action, a topic which has been substantively explored
but is not quite yet answered
\cite{russell1982collective,olsonlogic}.

@@

\subsubsection{\whatchanged}
\topic{The differences between crowd workers and pieceworkers seem defined largely by
the differences in the places of work.}
Whereas it arguably became inevitable that workers would have a place to
meet, discuss, and collaborate
when they began sharing places of work,
online spaces make it much harder to do so.
Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
without any affiliation with
--- or even knowledge of ---
communities of peers
% \ali{multiple citations that labor unions came out of factories here}
\cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

@@

\subsubsection{\implication}
\topic{What we've done in the field of crowd work might be able to tell us something about piecework
just as piecework has told us so much about crowd work.}
Crowd work research doesn't just benefit from
digital media allowing us to make
relationship networks like \citeauthor{crowdcollab} do;
we benefit from the firmer theoretical basis of Anthropology that
existed in a radically different form at the turn of the \nth{20} century,
when piecework began to emerge.
\citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works
\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
